### Ranking stability: Ranking variability via bootstrap approach

Blob plot of bootstrap results over the different tasks separated
by algorithm allows another perspective on the assessment data. This gives deeper insights into the characteristics
of tasks and the ranking uncertainty of the algorithms in each
task. 
<!-- 1000 bootstrap Rankings were performed for each task. -->
<!-- Each algorithm is considered separately and for each subtask (x-axis) all observed ranks across bootstrap samples (y-axis) are displayed. Additionally, medians and IQR is shown in black. -->

<!-- We see which algorithm is consistently among best, which is consistently among worst, which vary extremely... -->


\bigskip

```{r blobplot_bootstrap_byAlgorithm,fig.width=7,fig.height = 5}
#stabilityByAlgorithm.bootstrap.list
if (length(boot_object$matlist)<=6 &nrow((boot_object$matlist[[1]]))<=10 ){
  stabilityByAlgorithm(boot_object,
                       ordering=ordering_consensus,
                       max_size = 9,
                       size=4,
                       shape=4,
                       single = F) + scale_color_manual(values=cols)
} else {
  pl=stabilityByAlgorithm(boot_object,
                          ordering=ordering_consensus,
                          max_size = 9,
                          size=4,
                          shape=4,
                          single = T)
  for (i in 1:length(pl)) print(pl[[i]] +
                                  scale_color_manual(values=cols) +
                                  guides(size = guide_legend(title="%"),color="none")
                                )
}

```


<!-- Stacked frequencies of observed ranks across bootstrap samples are displayed with colouring according to subtask. Vertical lines provide original (non-bootstrap) rankings for each subtask. -->

An alternative representation is provided by a stacked
frequency plot of the observed ranks, separated by algorithm. Observed ranks across bootstrap samples are
displayed with coloring according to task. For algorithms that
achieve the same rank in different tasks for the full assessment
data set, vertical lines are on top of each other. Vertical lines
allow to compare the achieved rank of each algorithm over
different tasks.

\bigskip



```{r stackedFrequencies_bootstrap_byAlgorithm,fig.width=7,fig.height = 5}
#stabilityByAlgorithm.bootstrap.list
if (length(boot_object$matlist)<=6 &nrow((boot_object$matlist[[1]]))<=10 ){
  stabilityByAlgorithm(boot_object,
                       ordering=ordering_consensus,
                       stacked = TRUE,
                       single = F) 
} else {
  pl=stabilityByAlgorithm(boot_object,
                          ordering=ordering_consensus,
                          stacked = TRUE,
                          single = T)
  print(pl)
}

```
