---
params:
  object: NA
  colors: NA
  name: NULL
  consensus: NA
  isMultiTask: NA
  bootstrappingEnabled: NA
title: "Benchmarking report for `r params$name` "
author: "created by challengeR v`r packageVersion('challengeR')`  \nWiesenfarth, Reinke, Landman, Cardoso, Maier-Hein & Kopp-Schneider (2019)"
date: "`r Sys.setlocale('LC_TIME', 'English'); format(Sys.time(), '%d %B, %Y')`"
editor_options: 
  chunk_output_type: console
---

<!-- This text is outcommented -->
<!-- R code chunks start with "```{r }" and end with "```" -->
<!-- Please do not change anything inside of code chunks, otherwise any latex code is allowed -->

<!-- inline code with `r 0` -->


```{r setup, include=FALSE}
options(width=80)
out.format <- knitr::opts_knit$get("out.format")
img_template <- switch( out.format,
                     word = list("img-params"=list(dpi=150,
                                               fig.width=6,
                                               fig.height=6,
                                               out.width="504px",
                                               out.height="504px")),
                     {
                       # default
                       list("img-params"=list( fig.width=7,fig.height = 3,dpi=300))
                     } )

knitr::opts_template$set( img_template )

knitr::opts_chunk$set(echo = F,#fig.width=7,fig.height = 3,dpi=300,
                      fig.align="center")
theme_set(theme_light())

isMultiTask = params$isMultiTask
bootstrappingEnabled = params$bootstrappingEnabled

```


```{r }
object = params$object
if (isMultiTask) {
ordering_consensus=names(params$consensus)
} else
{
  ordering_consensus=names(sort(t(object$matlist[[1]][,"rank",drop=F])["rank",]))
}
color.fun=params$colors

```

```{r }

challenge_multiple=object$data
ranking.fun=object$FUN

cols_numbered=cols=color.fun(length(ordering_consensus))
names(cols)=ordering_consensus
names(cols_numbered)= paste(1:length(cols),names(cols))

if (bootstrappingEnabled) {
  boot_object = params$object
  challenge_multiple=boot_object$data

  ranking.fun=boot_object$FUN
  object=challenge_multiple%>%ranking.fun

  object$fulldata=boot_object$fulldata  # only not NULL if subset of algorithms used

  cols_numbered=cols=color.fun(length(ordering_consensus))
  names(cols)=ordering_consensus
  names(cols_numbered)= paste(1:length(cols),names(cols))
}


```


This document presents a systematic report on a benchmark study. Input data comprises raw metric values for all algorithms and test cases. Generated plots are:

```{r, child=if (!isMultiTask && !bootstrappingEnabled) system.file("appdir", "overviewSingleTaskNoBootstrapping.Rmd", package="challengeR")}

```

```{r, child=if (!isMultiTask && bootstrappingEnabled) system.file("appdir", "overviewSingleTaskBootstrapping.Rmd", package="challengeR")}

```

```{r, child=if (isMultiTask && !bootstrappingEnabled) system.file("appdir", "overviewMultiTaskNoBootstrapping.Rmd", package="challengeR")}

```

```{r, child=if (isMultiTask && bootstrappingEnabled) system.file("appdir", "overviewMultiTaskBootstrapping.Rmd", package="challengeR")}

```

```{r,results='asis'}

if (!isMultiTask && !is.null(object$fulldata[[1]])) {
  cat("Only top ",
      length(levels(challenge_multiple[[1]][[attr(challenge_multiple,"algorithm")]])),
      " out of ",
      length(levels(object$fulldata[[1]][[attr(challenge_multiple,"algorithm")]])),
      " algorithms visualized.\n")
}

```

Ranking of algorithms within tasks according to the following chosen ranking scheme:

```{r,results='asis'}
a=(  lapply(object$FUN.list,function(x) {
                 if (!is.character(x)) return(paste0("aggregate using function ",
                                                     paste(gsub("UseMethod","",
                                                                deparse(functionBody(x))),
                                                           collapse=" ")
                                                     ))
                 else if (x=="rank") return(x)
                 else return(paste0("aggregate using function ",x))
  }))
cat("&nbsp; &nbsp; *",paste0(a,collapse=" then "),"*",sep="")

if (is.character(object$FUN.list[[1]]) && object$FUN.list[[1]]=="significance") cat("\n\n Column 'prop.sign' is equal to the number of pairwise significant test results for a given algorithm divided by the number of algorithms.")
```

```{r,results='asis'}

if (isMultiTask) {
  cat("Ranking list for each task:\n")

  for (t in 1:length(object$matlist)){
    cat("\n",names(object$matlist)[t],": ")
    n.cases=nrow(challenge_multiple[[t]])/length(unique(challenge_multiple[[t]][[attr(challenge_multiple,"algorithm")]]))

    cat("\nAnalysis based on ",
        n.cases,
        " test cases which included",
        sum(is.na(challenge_multiple[[t]][[attr(challenge_multiple,"value")]])),
        " missing values.")

    x=object$matlist[[t]]
    print(knitr::kable(x[order(x$rank),]))
  }
} else {
  n.cases=nrow(challenge_multiple[[1]])/length(unique(challenge_multiple[[1]][[attr(challenge_multiple,"algorithm")]]))

  cat("\nAnalysis based on ",
      n.cases,
      " test cases which included",
      sum(is.na(challenge_multiple[[1]][[attr(challenge_multiple,"value")]])),
      " missing values.")

  cat("\n\nRanking list:")

  x=object$matlist[[1]]
  print(knitr::kable(x[order(x$rank),]))
}

```

\bigskip


```{r, child=if (isMultiTask) system.file("appdir", "consensusRanking.Rmd", package="challengeR")}

```


# Visualization of raw assessment data

```{r,results='asis'}

if (isMultiTask) {
  cat("Algorithms are ordered according to chosen ranking scheme for each task.")
}

```

## Dot- and boxplots

*Dot- and boxplots* for visualizing raw assessment data separately for each algorithm. Boxplots representing descriptive statistics over all test cases (median, quartiles and outliers) are combined with horizontally jittered dots representing individual test cases.

\bigskip

```{r boxplots}
temp=boxplot(object, size=.8)
temp=lapply(temp, function(x) utils::capture.output(x+xlab("Algorithm")+ylab("Metric value")))

```



## Podium plots
*Podium plots* (see also Eugster et al, 2008) for visualizing raw assessment data. Upper part (spaghetti plot): Participating algorithms are color-coded, and each colored dot in the plot represents a metric value achieved with the respective algorithm. The actual metric value is encoded by the y-axis. Each podium (here: $p$=`r length(ordering_consensus)`) represents one possible rank, ordered from best (1) to last (here: `r length(ordering_consensus)`). The assignment of metric values (i.e. colored dots) to one of the podiums is based on the rank that the respective algorithm achieved on the corresponding test case. Note that the plot part above each podium place is further subdivided into $p$ "columns", where each column represents one participating algorithm (here: $p=$ `r length(ordering_consensus)`).  Dots corresponding to identical test cases are connected by a line, leading to the shown spaghetti structure. Lower part: Bar charts represent the relative frequency for each algorithm to achieve the rank encoded by the podium place. 

```{r ,eval=T,fig.width=12, fig.height=6,include=FALSE}
plot.new()
algs=ordering_consensus
l=legend("topright", 
         paste0(1:length(algs),": ",algs), 
         lwd = 1, cex=1.4,seg.len=1.1,
         title="Rank: Alg.",
         plot=F) 

w <- grconvertX(l$rect$w, to='ndc') - grconvertX(0, to='ndc')
h<- grconvertY(l$rect$h, to='ndc') - grconvertY(0, to='ndc')
addy=max(grconvertY(l$rect$h,"user","inches"),6)
```


```{r podium,eval=T,fig.width=12, fig.height=addy}
#c(bottom, left, top, right

op<-par(pin=c(par()$pin[1],6),
        omd=c(0, 1-w, 0, 1),
        mar=c(par('mar')[1:3], 0)+c(-.5,0.5,-.5,0),
        cex.axis=1.5,
        cex.lab=1.5,
        cex.main=1.7)

oh=grconvertY(l$rect$h,"user","lines")-grconvertY(6,"inches","lines")
if (oh>0) par(oma=c(oh,0,0,0))


set.seed(38)
podium(object,
       col=cols,
       lines.show = T, lines.alpha = .4,
       dots.cex=.9,
       ylab="Metric value",
       layout.heights=c(1,.35),
       legendfn = function(algs, cols) {
                 legend(par('usr')[2], par('usr')[4], 
                 xpd=NA, 
                 paste0(1:length(algs),": ",algs), 
                 lwd = 1, col =  cols, 
                 bg = NA,
                 cex=1.4, seg.len=1.1,
                 title="Rank: Alg.") 
        }
      )
par(op)
  
```


## Ranking heatmaps
*Ranking heatmaps* for visualizing raw assessment data. Each cell $\left( i, A_j \right)$ shows the absolute frequency of test cases in which algorithm $A_j$ achieved rank $i$.

\bigskip

```{r rankingHeatmap,fig.width=9, fig.height=9,out.width='70%'}
temp=utils::capture.output(rankingHeatmap(object))
```



# Visualization of ranking stability

```{r, child=if (bootstrappingEnabled) system.file("appdir", "visualizationBlobPlots.Rmd", package="challengeR")}

```

```{r, child=if (bootstrappingEnabled) system.file("appdir", "visualizationViolinPlots.Rmd", package="challengeR")}

```


## *Significance maps* for visualizing ranking stability based on statistical significance

*Significance maps* depict incidence matrices of
pairwise significant test results for the one-sided Wilcoxon signed rank test at a 5\% significance level with adjustment for multiple testing according to Holm. Yellow shading indicates that metric values of the algorithm on the x-axis were significantly superior to those from the algorithm on the y-axis, blue color indicates no significant difference.


\bigskip

```{r significancemap,fig.width=6, fig.height=6,out.width='200%'}
temp=utils::capture.output(significanceMap(object,alpha=0.05,p.adjust.method="holm")
        )

```

<!-- \subsubsection{Hasse diagram} -->

<!-- ```{r single_stability_significance_hasse, fig.height=19} -->
<!-- plot(relensemble) -->
<!-- ``` -->




## Ranking robustness to ranking methods
*Line plots* for visualizing rankings robustness across different ranking methods. Each algorithm is represented by one colored line. For each ranking method encoded on the x-axis, the height of the line represents the corresponding rank. Horizontal lines indicate identical ranks for all methods.

\bigskip

```{r lineplot,fig.width=7,fig.height = 5}
if (length(object$matlist)<=6 &nrow((object$matlist[[1]]))<=10 ){
  methodsplot(challenge_multiple,
              ordering = ordering_consensus,
              na.treat=object$call[[1]][[1]]$na.treat) + scale_color_manual(values=cols)
}else {
  x=challenge_multiple
  for (subt in names(challenge_multiple)){
     dd=as.challenge(x[[subt]],
                     value=attr(x,"value"), 
                     algorithm=attr(x,"algorithm") ,
                     case=attr(x,"case"),
                     annotator = attr(x,"annotator"), 
                     by=attr(x,"by"),
                     smallBetter = !attr(x,"largeBetter"),
                     na.treat=object$call[[1]][[1]]$na.treat
                     )
 
    print(methodsplot(dd,
                      ordering = ordering_consensus) + scale_color_manual(values=cols)
          )
  }
}
```



```{r, child=if (isMultiTask) system.file("appdir", "visualizationAcrossTasks.Rmd", package="challengeR")}

```



# References

Wiesenfarth, M., Reinke, A., Landman, B.A., Cardoso, M.J., Maier-Hein, L. and Kopp-Schneider, A. (2019). Methods and open-source toolkit for analyzing and visualizing challenge results. *arXiv preprint arXiv:1910.05121*

M. J. A. Eugster, T. Hothorn, and F. Leisch, “Exploratory
and inferential analysis of benchmark experiments,”
Institut fuer Statistik, Ludwig-Maximilians-
Universitaet Muenchen, Germany, Technical Report 30,
2008. [Online]. Available: http://epub.ub.uni-muenchen.
de/4134/.
