---
params:
  object: NA
  colors: NA
  name: NULL
  consensus: NA
title: "Benchmarking report for `r params$name` "
author: created by challengeR `r packageVersion('challengeR')` (Wiesenfarth, Reinke, Cardoso, Maier-Hein & Kopp-Schneider, 2019)
date: "`r Sys.setlocale('LC_TIME', 'English'); format(Sys.time(), '%d %B, %Y')`"
editor_options: 
  chunk_output_type: console
---

<!-- This text is outcommented -->
<!-- R code chunks start with "```{r }" and end with "```" -->
<!-- Please do not change anything inside of code chunks, otherwise any latex code is allowed -->

<!-- inline code with `r 0` -->


```{r setup, include=FALSE}
options(width=80)
out.format <- knitr::opts_knit$get("out.format")
img_template <- switch( out.format,
                     word = list("img-params"=list(dpi=150,
                                               fig.width=6,
                                               fig.height=6,
                                               out.width="504px",
                                               out.height="504px")),
                     {
                       # default
                       list("img-params"=list( fig.width=7,fig.height = 3,dpi=300))
                     } )

knitr::opts_template$set( img_template )

knitr::opts_chunk$set(echo = F,#fig.width=7,fig.height = 3,dpi=300,
                      fig.align="center")
theme_set(theme_light())

```


```{r }
object = params$object
ordering_consensus=names(params$consensus)
color.fun=params$colors

```

```{r }
challenge_multiple=object$data

ranking.fun=object$FUN

cols_numbered=cols=color.fun(length(ordering_consensus))
names(cols)=ordering_consensus
names(cols_numbered)= paste(1:length(cols),names(cols))


```


This document presents a systematic report on a benchmark study. Input data comprises raw metric values for all algorithms and test cases. Generated plots are:

* Visualization of assessment data: Dot- and boxplots, podium plots and ranking heatmaps
* Visualization of ranking robustness: Line plots
* Visualization of ranking stability: Significance maps
* Visualization of cross-task insights


Ranking of algorithms within tasks according to the following chosen ranking scheme:

```{r,results='asis'}
a=(  lapply(object$FUN.list,function(x) {
 #    if (!is.character(x)) return(paste0("Aggregate using function ",paste(capture.output(x),collapse=" ")))
     if (!is.character(x)) return(paste0("aggregate using function ",paste(gsub("UseMethod","",deparse(functionBody(x))),collapse=" ")))
 #    if (!is.character(x)) return(paste0("Aggregate using function ",paste(gsub("UseMethod","",deparse(functionBody(x))),collapse=" ")))
     else if (x=="rank") return(x)
     else return(paste0("aggregate using function ",x))
   }))
#cat("1.",paste(a,collapse="\n2. "))
cat("&nbsp; &nbsp; *",paste0(a,collapse=" then "),"*",sep="")

if (is.character(object$FUN.list[[1]]) && object$FUN.list[[1]]=="significance") cat("\n\n Column 'prop.sign' is equal to the number of pairwise significant test results for a given algorithm divided by the number of algorithms.")
```


Ranking list for each task:
```{r,results='asis'}
#object
for (t in 1:length(object$matlist)){
 cat("\n",names(object$matlist)[t],": ")
 n.cases=nrow(challenge_multiple[[t]])/length(unique(challenge_multiple[[t]][[attr(challenge_multiple,"algorithm")]]))
  cat("\nAnalysis based on ", n.cases," test cases which included", sum(is.na(challenge_multiple[[t]][[attr(challenge_multiple,"value")]]))," missing values.")
  x=object$matlist[[t]]
  print(knitr::kable(x[order(x$rank),]))
}
#lapply(object$matlist, function(x) knitr::kable(x[order(x$rank),]))

```

\bigskip

Consensus ranking according to chosen method `r attr(params$consensus,"method")`:
```{r}
knitr::kable(data.frame(value=round(params$consensus,3), rank=rank(params$consensus, ties.method="min")))
```


# Visualization of raw assessment data
Algorithms are ordered according to chosen ranking scheme for each task.

## Dot- and boxplots

*Dot- and boxplots* for visualizing raw assessment data separately for each algorithm. Boxplots representing descriptive statistics over all test cases (median, quartiles and outliers) are combined with horizontally jittered dots representing individual test cases.

\bigskip

```{r boxplots}
#temp=boxplot(challenge_multiple,size=.8)
temp=boxplot(object,size=.8)
temp=lapply(temp,function(x) utils::capture.output(x+xlab("Algorithm")+ylab("Metric value")))

```



## Podium plots
*Podium plots* (see also Eugster et al, 2008) for visualizing raw assessment data. Upper part (spaghetti plot): Participating algorithms are color-coded, and each colored dot in the plot represents a metric value achieved with the respective algorithm. The actual metric value is encoded by the y-axis. Each podium (here: $p$=`r length(ordering_consensus)`) represents one possible rank, ordered from best (1) to last (here: `r length(ordering_consensus)`). The assignment of metric values (i.e. colored dots) to one of the podiums is based on the rank that the respective algorithm achieved on the corresponding test case. Note that the plot part above each podium place is further subdivided into $p$ "columns", where each column represents one participating algorithm (here: $p=$ `r length(ordering_consensus)`).  Dots corresponding to identical test cases are connected by a line, leading to the shown spaghetti structure. Lower part: Bar charts represent the relative frequency for each algorithm to achieve the rank encoded by the podium place. 

```{r ,eval=T,fig.width=12, fig.height=6,include=FALSE}
plot.new()
algs=ordering_consensus#rownames(boot_object$matlist[[1]])
l=legend("topright", paste0(1:length(algs),": ",algs), lwd = 1, cex=1.4,seg.len=1.1,title="Rank: Alg.",plot=F) 
w <- grconvertX(l$rect$w, to='ndc') - grconvertX(0, to='ndc')
h<- grconvertY(l$rect$h, to='ndc') - grconvertY(0, to='ndc')
addy=max(grconvertY(l$rect$h,"user","inches"),6)#+5
```


```{r podium,eval=T,fig.width=12, fig.height=addy}
# gg_color_hue <- function(n) {
#   hues = seq(15, 375, length = n + 1)
#   hcl(h = hues, l = 65, c = 100)[1:n]
# }
# 
# cols = gg_color_hue(n)


#c(bottom, left, top, right
#par(mar=c(5, 4, 4, 2) + 0.1,cex.axis=1.5,cex.lab=1.5,cex.main=1.7)
#op <-par(mar=par()$mar+c(-.5,0.5,-.5,4.5))

op<-par(pin=c(par()$pin[1],6),omd=c(0, 1-w, 0, 1),mar=c(par('mar')[1:3], 0)+c(-.5,0.5,-.5,0),cex.axis=1.5,cex.lab=1.5,cex.main=1.7)#,mar=c(5, 4, 4, 2) + 0.1)
oh=grconvertY(l$rect$h,"user","lines")-grconvertY(6,"inches","lines")
if (oh>0) par(oma=c(oh,0,0,0))


  set.seed(38)
 podium(object,
  # boot_object$data,
 #       ranking.fun=boot_object$FUN, 
   col=cols,
        lines.show = T,lines.alpha = .4,
        dots.cex=.9,ylab="Metric value",layout.heights=c(1,.35),
          legendfn = function(algs, cols) {
            #title(single_subtask); 
  #          legend("topright", inset=c(-0.12,0), xpd=TRUE, algs, lwd = 1, col =  cols, bg = NA,cex=1.4,seg.len=1.1) 
          legend(par('usr')[2], par('usr')[4], xpd=NA, paste0(1:length(algs),": ",algs), lwd = 1, col =  cols, bg = NA,cex=1.4,seg.len=1.1,title="Rank: Alg.") 
        }
          )
par(op)
  
```


## Ranking heatmaps
*Ranking heatmaps* for visualizing raw assessment data. Each cell $\left( i, A_j \right)$ shows the absolute frequency of test cases in which algorithm $A_j$ achieved rank $i$.

\bigskip

```{r rankingHeatmap,fig.width=9, fig.height=9,out.width='70%'}
rankingHeatmap(object)
```



# Visualization of ranking stability





## *Significance maps* for visualizing ranking stability based on statistical significance

*Significance maps* depict incidence matrices of
pairwise significant test results for the one-sided Wilcoxon signed rank test at a 5\% significance level with adjustment for multiple testing according to Holm. Yellow shading indicates that metric values of the algorithm on the x-axis were significantly superior to those from the algorithm on the y-axis, blue color indicates no significant difference.


\bigskip

```{r significancemap,fig.width=6, fig.height=6,out.width='200%'}
#```{r single_stability_significance_table1b,fig.width=4, fig.height=4,out.width='50%'}
# a=challenge_multiple%>%decision.challenge(p.adjust.method="holm")
# aa=lapply(a,as.relation.challenge.incidence)
# names(aa)=names(challenge_multiple)
# 
# relensemble= do.call(relation_ensemble,args = aa)
# 
# 
# for (Task in names(object$data)){
#   print(significanceMap(rankedMat=object$matlist[[Task]],
#                  relation_object=relensemble[[Task]]
#                  )+ggtitle(Task)+ theme(aspect.ratio=1))#+scale_color_manual(name="decision",values=c("white","lightblue")))
#   
# }


temp=utils::capture.output(significanceMap(object,alpha=0.05,p.adjust.method="holm")
        )

```

<!-- \subsubsection{Hasse diagram} -->

<!-- ```{r single_stability_significance_hasse, fig.height=19} -->
<!-- plot(relensemble) -->
<!-- ``` -->




## Ranking robustness to ranking methods
*Line plots* for visualizing rankings robustness across different ranking methods. Each algorithm is represented by one colored line. For each ranking method encoded on the x-axis, the height of the line represents the corresponding rank. Horizontal lines indicate identical ranks for all methods.

\bigskip

```{r lineplot,fig.width=7,fig.height = 5}


if (length(object$matlist)<=6 &nrow((object$matlist[[1]]))<=10 ){
  methodsplot(challenge_multiple,ordering = ordering_consensus)+scale_color_manual(values=cols)
} else {
  x=challenge_multiple
  for (subt in names(challenge_multiple)){
     dd=as.challenge(x[[subt]],value=attr(x,"value"), algorithm=attr(x,"algorithm") ,case=attr(x,"case"),
                      annotator = attr(x,"annotator"), by=attr(x,"by"),
                      smallBetter = !attr(x,"largeBetter"))
 
    print(methodsplot(dd,ordering = ordering_consensus)+scale_color_manual(values=cols))
  }
}
```





# Visualization of cross-task insights

Algorithms are ordered according to consensus ranking.




## Characterization of algorithms

### Ranking stability: Variability of achieved rankings across tasks
<!-- Variability of achieved rankings across tasks: If a -->
<!-- reasonably large number of tasks is available, a blob plot -->
<!-- can be drawn, visualizing the distribution -->
<!-- of ranks each algorithm attained across tasks. -->
<!-- Displayed are all ranks and their frequencies an algorithm -->
<!-- achieved in any task. If all tasks would provide the same -->
<!-- stable ranking, narrow intervals around the diagonal would -->
<!-- be expected. -->

<!-- blob plot similar to the one shown in Fig.~\ref{blobByTask} substituting rankings based on bootstrap samples with the rankings corresponding to multiple tasks. This way, the distribution of ranks across tasks can be intuitively visualized. -->


\bigskip

```{r blobplot_raw}
#stability.ranked.list
stability(object,ordering=ordering_consensus,max_size=9,size=8,shape=4)+scale_color_manual(values=cols)
```




## Characterization of tasks



### Cluster Analysis
<!-- Quite a different question of interest -->
<!-- is to investigate the similarity of tasks with respect to their -->
<!-- rankings, i.e., which tasks lead to similar ranking lists and the -->
<!-- ranking of which tasks are very different. For this question -->
<!-- a hierarchical cluster analysis is performed based on the -->
<!-- distance between ranking lists. Different distance measures -->
<!-- can be used (here: Spearman's footrule distance) -->
<!-- as well as different agglomeration methods (here: complete and average).  -->


Dendrogram from hierarchical cluster analysis} and \textit{network-type graphs} for assessing the similarity of tasks based on challenge rankings. 

A dendrogram is a visualization approach based on hierarchical clustering. It depicts clusters according to a chosen distance measure (here: Spearman's footrule) as well as a chosen agglomeration method (here: complete and average agglomeration). 
\bigskip

```{r , fig.width=6, fig.height=5,out.width='60%'}
#d=relation_dissimilarity.ranked.list(object,method=kendall)

# use ranking list
  relensemble=as.relation.ranked.list(object)
 
# # use relations
#   a=challenge_multi%>%decision.challenge(p.adjust.method="none")
#   aa=lapply(a,as.relation.challenge.incidence)
#   names(aa)=names(challenge_multi)
#   relensemble= do.call(relation_ensemble,args = aa)
d <- relation_dissimilarity(relensemble, method = "symdiff")
```

  
```{r dendrogram_complete, fig.width=6, fig.height=5,out.width='60%'}
if (length(relensemble)>2) {
  plot(hclust(d,method="complete")) #,main="Symmetric difference distance - complete"
} else cat("\nCluster analysis only sensible if there are >2 tasks.\n\n")
```

\bigskip


```{r dendrogram_average, fig.width=6, fig.height=5,out.width='60%'}
if (length(relensemble)>2) plot(hclust(d,method="average")) #,main="Symmetric difference distance - average"
```

<!-- An alternative representation of -->
<!-- distances between tasks (see Eugster et al, 2008) is provided by networktype -->
<!-- graphs. -->
<!-- Every task is represented by a node and nodes are connected -->
<!-- by edges. Distance between nodes increase exponentially with -->
<!-- the chosen distance measure d (here: distance between nodes -->
<!-- equal to 1:05d). Thick edges represent smaller distance, i.e., -->
<!-- the ranking lists of corresponding tasks are similar. Tasks with -->
<!-- a unique winner are filled to indicate the algorithm. In case -->
<!-- there are more than one first-ranked algorithm, nodes remain -->
<!-- uncoloured. -->


In network-type graphs (see Eugster et al, 2008), every task is represented by a node and nodes are connected by edges whose length is determined by a chosen distance measure. Here, distances between nodes are chosen to increase exponentially in Spearman's footrule distance with growth rate 0.05 to accentuate large distances.
Hence, tasks that are similar with respect to their algorithm ranking appear closer together than those that are dissimilar. Nodes representing tasks with a unique winner are colored-coded by the winning algorithm. In case there are more than one first-ranked algorithms in a task, the corresponding node remains uncolored.
\bigskip

```{r ,eval=T,fig.width=12, fig.height=6,include=FALSE}
if (length(relensemble)>2) {
  netw=network(object,
               method = "symdiff", 
               edge.col=grDevices::grey.colors,
               edge.lwd=1,
               rate=1.05,
               cols=cols
               )
  
  plot.new()
  leg=legend("topright",  names(netw$leg.col), lwd = 1, col = netw$leg.col, bg =NA,plot=F,cex=.8)
  w <- grconvertX(leg$rect$w, to='inches')
  addy=6+w
} else addy=1

```

```{r network, fig.width=addy, fig.height=6,out.width='100%'}
if (length(relensemble)>2) {
  plot(netw,
       layoutType = "neato",
       fixedsize=TRUE,
       # fontsize,
       # width,
       # height,
       shape="ellipse",
       cex=.8
       )
}

```


# Reference

Wiesenfarth, M., Reinke, A., Landmann A.L., Cardoso, M.J., Maier-Hein, L. and Kopp-Schneider, A. (2019). Methods and open-source toolkit for analyzing and visualizing challenge results. *arXiv preprint arXiv:1910.05121*

M. J. A. Eugster, T. Hothorn, and F. Leisch, “Exploratory
and inferential analysis of benchmark experiments,”
Institut fuer Statistik, Ludwig-Maximilians-
Universitaet Muenchen, Germany, Technical Report 30,
2008. [Online]. Available: http://epub.ub.uni-muenchen.
de/4134/.







